---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ksamplesLTRC

<!-- badges: start -->
<!-- badges: end -->

ksamplesLTRC provides nonparametric k-sample tests for comparing distributions
under left truncation and/or right censoring. It implements 
Kolmogorov--Smirnov-type, Cramér--von Mises-type, and weighted log-rank
statistics, with bootstrap-based p-value approximation, for one or more
independent samples of possibly truncated and/or censored survival data.

## Installation

You can install ksamplesLTRC from CRAN with:

``` r
install.packages("ksamplesLTRC")
```

## Example

A basic k-sample comparison under left truncation and right censoring, 
using the well-known `channing` dataset from the `KMsurv` package:

```{r example}
library(ksamplesLTRC)
library(KMsurv)
data(channing)

data.channing <- data.frame(channing$ageentry, 
                            channing$age,
                            channing$death, 
                            channing$gender)

aa <- ltrc.test(data.channing,
                holes='conditional',
                tests=c('ks','cvm','logrank'),
                B = 200,
                p=c(0,1,0.5,0),
                q=c(0,0,0.5,1))
plot(aa)
summary(aa)
```
